Critical Transitions in Metapopulation Connectivity

### 2020-09-07 writing/manuscript.tex
ok

@@

\title{Phase Transitions in Landscape Connectivity}
\author[1,2]{M.D. Catchen}
\author[1]{S.M. Flaxman}
\affil[1]{\small{Department of Ecology and Evolutionary Biology, University of Colorado at Boulder}}
\affil[2]{\small{Department of Biology, McGill University}}
\date{\today}

@@

\end{abstract}
\clearpage

\section{Introduction}

@@

\section{What are phase transitions?}

@@

\begin{equation} \label{diffusion_model}
  d \boldsymbol{N} = \boldsymbol{I} (D^T \boldsymbol{N})\bigg(\boldsymbol{I}\boldsymbol{K}^{-1}(\boldsymbol{K}-D^T \boldsymbol{N})\bigg) d\boldsymbol{t} + \boldsymbol{I}\boldsymbol{\sigma} \boldsymbol{N} \ d\boldsymbol{W}
\end{equation}

@@

\hypertarget{measuring-synchrony}{%
\subsubsection{Measuring Synchrony}\label{measuring-synchrony}}

@@

\hypertarget{simulating-a-phase-transition-across-a-migration-gradient}{%
\subsubsection{Simulating a Phase Transition across a Migration
Gradient}\label{simulating-a-phase-transition-across-a-migration-gradient}}

@@

\pagebreak
\begin{figure}
    \includegraphics[width=15cm]{figs/figure3}
    \caption{}
    \label{}
\end{figure}

\begin{figure}
    \includegraphics[width=15cm]{figs/figure4}
    \caption{}
    \label{}
\end{figure}

\begin{figure}
    \includegraphics[width=15cm]{figs/figure5}
    \caption{}
    \label{}
\end{figure}

>>>>

\setcounter{secnumdepth}{3}
\addtocontents{toc}{\setcounter{tocdepth}{2}}

@@

\title{Critical Transitions in Metapopulation Connectivity}
\author[1,2]{M.D. Catchen}
\author[1]{S.M. Flaxman}
\affil[1]{\small{Department of Ecology and Evolutionary Biology, University of Colorado at Boulder}}
\affil[2]{\small{Department of Biology, McGill University}}
\date{\today}

@@

\end{abstract}
\clearpage
\tableofcontents
\clearpage
\section{Introduction}

@@

@@

\begin{equation} \label{diffusion_model}
    dN_i = \sum_j \bigg[ D_{ji} \lambda_i N_i \bigg(1-\frac{N_i}{K_i}\bigg)  \bigg] dt + \sigma N_i dW_i
\end{equation}

@@

\hypertarget{measuring-synchrony}{%
\subsection{Measuring Synchrony}\label{measuring-synchrony}}

@@

\hypertarget{simulating-a-phase-transition-across-a-migration-gradient}{%
\subsection{Simulating a Phase Transition across a Migration
Gradient}\label{simulating-a-phase-transition-across-a-migration-gradient}}

@@

\hypertarget{phase-transitions-across-a-migration-gradient}{%
\section{Synchrony Across a Migration Gradient}\label{phase-transitions-across-a-migration-gradient}}

Probability distribution of synchrony in a set of populations $L$ given $\alpha$ and $m$.

There is symmetry in these distributions around $m = 1 - \frac{1}{|L|}$

\pagebreak
\begin{figure}[h]
    \includegraphics[width=15cm]{figs/figure3}
    \caption{}
    \label{}
\end{figure}

\begin{figure}[h]
    \includegraphics[width=15cm]{figs/figure4}
    \caption{}
    \label{}
\end{figure}

\begin{figure}[h]
    \includegraphics[width=15cm]{figs/figure5}
    \caption{}
    \label{}
\end{figure}

\hypertarget{critical-transitions-across-space}{%
\section{Critical Transitions in Synchrony Across Space}\label{critical-transitions-across-space}}

\hypertarget{simulating-a-phase-transition-across-a-migration-gradient}{%
\subsection{Landscape Connectivity}\label{simulating-a-phase-transition-across-a-migration-gradient}}

\begin{figure}
    \includegraphics[width=15cm]{figs/figure9}
    \caption{}
    \label{}
\end{figure}

\hypertarget{simulating-a-phase-transition-across-a-migration-gradient}{%
\subsection{Landscape Subdivision}\label{simulating-a-phase-transition-across-a-migration-gradient}}

\begin{figure}
    \includegraphics[width=15cm]{figs/figure10}
    \caption{}
    \label{}
\end{figure}

\hypertarget{conclusion}{%
\section{Conclusion}\label{conclusion}}
